Naturalness in U(1) extensions of the MSSM

### 2014-12-02 paper/e6ssm-tuning-paper.tex
Removed unfinished equation so that it isn't forgotten about and left unfinished
added recent baryogensis paper.
Fixed minor typos

In this paper we will often focus on a very well motivated $E_6$
inspired $U(1)$ extension, the Exceptional Supersymmetric Standard
Model (E$_6$SSM)\cite{King:2005jy,King:2005my,Athron:2010zz}.  In this
model since the right handed neutrino remains interaction-less they may
explain the tiny observed masses of neutrinos via the see-saw
mechanism and the baryon asymmetry in the universe via leptogenesis
\cite{Hambye:2000bn,King:2008qb, King:2008gw}.

@@

Written in the form of Eq. (\ref{eq:E6MZequation}) we see the potential new source of fine tuning alluded to above, in the form of the third term on the right-hand side. For large values of the VEV $s$, the $D$-term contributions can be quite a bit larger than $M_Z^2$. In particular, recent experimental limits \cite{Aad:2014cka} require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in $U(1)_\chi$ models. To satisfy these limits typically requires large values of $s$, for example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_u}|,|D_{H_d}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$. As a result the remaining terms on the right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel the resulting very large contribution to $M_Z$. Moreover, because this is a large \textit{tree level} fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners.

@@

To quantify the resulting fine tuning we apply the traditional Ellis-Barbieri-Giudice measure \cite{Ellis:1986yg,Barbieri:1987fn}. A specific model is characterised by a set of $n$ model parameters $\{p_i\}$ and is defined at some input scale $M_X$. For a given parameter $p$ in this set, one computes an associated sensitivity coefficient \cite{Feng:2013pwa}

@@

continue to hold under an arbitrary variation in a model parameters $p\rightarrow p+\delta p$, so that the variations $\delta f_i$ satisfy

@@

\beta_{\lambda}^{(2)}&=\lambda

>>>>

In this paper we will often focus on a very well motivated $E_6$
inspired $U(1)$ extension, the Exceptional Supersymmetric Standard
Model (E$_6$SSM)\cite{King:2005jy,King:2005my,Athron:2010zz}.  In this
model since the right handed neutrino remains interaction-less they may
explain the tiny observed masses of neutrinos via the see-saw
mechanism and the baryon asymmetry in the universe via leptogenesis
\cite{Hambye:2000bn,King:2008qb, King:2008gw}.  Recently it has also been studied in the context of electroweak baryogenesis \cite{Chao:2014hya}.

@@

Written in the form of Eq. (\ref{eq:E6MZequation}) we see the potential new source of fine tuning alluded to above, in the form of the third term on the right-hand side. For large values of the VEV $s$, the $D$-term contributions can be quite a bit larger than $M_Z^2$. In particular, recent experimental limits \cite{Aad:2014cka} require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in $U(1)_\chi$ models. To satisfy these limits typically requires large values of the singlet VEV $s$. For example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_u}|,|D_{H_d}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$. As a result the remaining terms on the right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel the resulting very large contribution to $M_Z$. Moreover, because this is a large \textit{tree level} fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners.

@@

As stated above, in order to quantify the resulting fine tuning we apply the traditional Ellis-Barbieri-Giudice measure \cite{Ellis:1986yg,Barbieri:1987fn}. A specific model is characterised by a set of $n$ model parameters $\{p_i\}$ and is defined at some input scale $M_X$. For a given parameter $p$ in this set, one computes an associated sensitivity coefficient \cite{Feng:2013pwa}

@@

continue to hold under an arbitrary variation in a model parameter $p\rightarrow p+\delta p$, so that the variations $\delta f_i$ satisfy

@@
